\section*{Experience}

\begin{workentry}{Freelance Software Developer}{Self-Employed}{Remote}{Jun 2026 -- Present}
  \item Design and build custom software solutions for companies and private clients, automating processes and delivering digital products end-to-end.
  \item Deliver clean, maintainable code across web applications, desktop tools, backend systems, and APIs using PostgreSQL and Doctrine, tailored to each client's requirements.
\end{workentry}

\begin{workentry}{Website Administrator}{Naturfreunde Österreich}{Remote}{Jan 2023 -- Feb 2026}
  \item Owned end-to-end administration and maintenance of the official website for the local Neubau group.
  \item Managed content updates and performed regular maintenance to ensure technical stability.
  \item Optimized the CMS-based platform to deliver a reliable, engaging digital presence for the community.
\end{workentry}

\begin{workentry}{Network Engineering Intern}{CANCOM Austria}{Vienna, Austria (Hybrid)}{Aug 2024 -- Aug 2024}
  \item Earned the Fortinet NSE 3 certification, deepening expertise in network security concepts and infrastructure.
  \item Engineered Python scripts for network automation, improving operational efficiency and reliability.
\end{workentry}

\begin{workentry}{Network Engineering Intern}{CANCOM Austria}{Vienna, Austria (Hybrid)}{Aug 2023 -- Aug 2023}
  \item Configured and managed Cisco switches alongside Palo Alto Networks and Fortinet FortiGate firewalls in complex network environments.
  \item Earned Fortinet NSE 1 and NSE 2 certifications, demonstrating strong fundamentals in cybersecurity and threat mitigation.
\end{workentry}
